%%-------------Vita---------------------------------
\clearpage
\phantomsection  % correct link in PDF bookmarks.
\addtocontents{toc}{\cftpagenumbersoff{chapter}}  % omit page # in ToC
\addcontentsline{toc}{chapter}{Vita}
\chapter*{Vita}
\pagestyle{empty}
\thispagestyle{empty}
\singlespacing
Candidate's full name: Nasrin Eshraghi Ivari\\
University attended: \\

University of New Brunswick, Fredericton Campus, Degree in Geodesy and Geomatics Engineering, 2021.\\

University attended: Universiti Putra Malaysia, Graduated with a Degree in Computer Science, 2013\\

University attended: Azad University of Mashhad, Graduated with a Degree in B.Eng. in Software Engineering, 2009\\


Publications:\\

Ivari, N. E., Wachowicz, M., Agnew, T., \& Williams, P. A. (2020, October). Spatio-temporal Data Streaming with Affinity Propagation. Paper presented at AutoCarto 2020, the 23rd International Research Symposium on cartography and GIScience.\\


Young, S., Demmings, A., Ivari, N. E., Legault, J. P., \& Kent, K. B. (2019, October). Verilog Loop Unrolling, Module Generation, Part-Select and Arithmetic Right Shift Support in Odin II. In Proceedings of the 30th International Workshop on Rapid System Prototyping (RSP'19) (pp. 71-74).\\


Ivari, N. E, Kent, K. B. (2019, April). Improving the Verilog-to-Routing FPGA CAD flow. 6th Annual Faculty of Computer Science Research Exposition.\\


% Ivari, N. E. (March, 2016). Using Splay tree for traffic management system-based on UPM University campus. 2nd International Conference on Knowledge-Based Research in Computer Engineering and Information Technology.
